The Quantum Sneakernet

### 2019-01-16 Simon's section/main.tex
Some quotes and editing
Sneaker net editing

The development of a model for the quantum internet \cite{?} has a distinct advantage over all other communication networks that have preceded it, namely the ability to leverage a treasure trove of information about how global communications systems are used, what are their inefficiencies, their choke points and vulnerabilities. The knowledge that we have gained gives an interesting opportunity in the quantum space, namely, 
\\
\\
\textbf{If we had the ability to redesign the classical internet from scratch, how would we do it?}
\\
\\
The hardware that will be needed to transmit quantum information around the globe will be a parallel network to the classical internet as at the very least a fast classical network is still needed to relay the required information to make any quantum communications channel work \cite{?}. So, at a minimum, we can conclude that a global quantum network will be \textit{rate limited} by the classical networking infrastructure that supports it. However, considering that the classical internet currently has the capacity to transmit information at approximately 70\% of the speed of light (in standard silica fibre optics), over global distances and can do so at extremely high data rates means that we will have to work very hard to design and build large-scale quantum networks before the classical side-channel produces any significant bottlenecks.

@@

If these three core points are adhered to, the encrypted message is completely unbreakable by any adversary who may intercept it, regardless of any hypothetical computational resources they may have -- \textit{information-theoretic security}. Unfortunately, the above conditions are simply not practical in most real world situations. 
\begin{itemize}
\item Generating a random bit string, in the true definition of random, has only become technologically possible in the past decade or two as result of quantum technology. Quantum random number generators use the intrinsic randomness of quantum mechanical processes to generate random bit strings that for all intents and purposes are sufficient for one time pads. These devices can now be bought as off the shelf units with varying degrees of quality. 
\item Avoiding the reuse of a key can, in principle, be adhered to; but satisfying this requirement may be economically or logistically impractical. Avoiding reuse becomes even more difficult when the message to be encrypted is big. There are many examples of technology in the field that require secure, high data-rate transmission. Video footage from helicopters or drones is a good example. A drone equipped with a high-resolution 4K camera system needs to be able to transmit information at a rate of 764 GB/hour uncompressed. This would require the same rate of one-time-pad material to be generated and shared between Alice and Bob to ensure a secure connection of the video stream. None of this material could be used even a second time. 
\item The third and most vulnerable constraint is the sharing of key information between Alice and Bob in a manner that can be guaranteed to have never been compromised. This is complicated by the fact that Alice and Bob in almost all practical situations will not be in physical contact with each other prior to sharing an encrypted message. How can we exchange a large amount of key material between two parties who have never met in such a way that we can be as certain as humanly possible that the key information was not revealed, sold, copied or otherwise accessed by a third party? The third party may even be authorised to have access to the key information. This would immediately destroy the \textit{perfectly implemented} assumption underlying the security of the one-time-pad. 
\end{itemize}

@@

For extremely sensitive tasks, key-exchange and security is usually achieved through some combination of segregated networking and obfuscation. Here are some examples:

@@

\subsection{QKD versus classical key exchange techniques}\index{Classical key exchange}

A 2016 assessment from the UK agency GCHQ\index{GCHQ} references four concerns with QKD as an effective replacement for classical techniques. These concerns are:
\begin{itemize}
\item \textit{QKD protocols address only the problem of agreeing on keys for encrypting data.} Ubiquitous on-demand modern services (such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates) rely more on authentication and integrity mechanisms — such as digital signatures — than on encryption.
\item \textit{The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission and the fact that BB84 and similar proposals are fundamentally point-to-point protocols.} This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.
\item \textit{Hardware is relatively expensive to obtain and maintain.} Unlike software, hardware cannot be patched remotely or cheaply when it degrades or when vulnerabilities are discovered.
\item \textit{Any real-world QKD system will be built from classical components, such as sources, detectors, fibres, and ancillary classical network devices, any one of which may prove to be a weak link.} A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.
\item \textit{Denial of service (DoS) attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies.} Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.
\end{itemize}

@@

Colour centres, at least from the context of building large-portable qubit arrays, appear the most promising -- mostly due to to the large-scale infrastructure needed for the technology. In colour centres, an atomic defect is inserted within a crystal substrate -- for example, a Nitrogen defect in a perfect diamond crystal of Carbon -- which provides what is known as a \textit{spin vacuum} substrate. Essentially, the surrounding crystal itself provides the same isolation properties that an actual physical vacuum does in, for example, ion-trap technology. Additionally, many colour centres are operated at temperatures of only 4K. While still cold, 4K cryogenic technology is far simpler than the dilution refrigeration systems needed for a 30mK thermal environment. 4K cryogenic technology is so advanced that we are able to effectively launch these sorts of cooling systems into space. Thirdly, colour centres are generally \textit{optically accessible.}. An optically accessible colour centre has, in general, an electronic transition of the donor system that is resonant at optical frequencies. This allows for remote coupling of colour centres using optical photons which are comparatively easy to route in and out of the crystal and surrounding 4K infrastructure -- in comparison to superconducting qubits which interact with microwave photons which are difficult to route around or systems such as Phosphorus in Silicon that generally utilise direct dipole/dipole or exchange based coupling to realise gates.

@@

The surface code has been extremely well studied over the past 15 years. We have extremely accurate simulations that detail the threshold behaviour of the code under a variety of different assumptions and we have quantified very well how the scaling of the code behaves as a function of physical error rate. For this reason we are able to quantify expected \textit{logical} memory time, $T$, in terms of the physical operation time of the quantum gates in our hardware, $t$, the number of physical qubits in the QMU array, $N$, and the logical error rate we want to target, $P$. Through direct numerical simulation, we find:
\begin{align} \label{eq:scale}
T \approx 10t\sqrt{N} P(70p)^{-\sqrt{N}/4},
\end{align}
where $p$ is the physical error rate associated with each of the qubits within each QMU -- assumed to be at least below the Fault-tolerant threshold of the planar code, $p_{th} \approx 0.7\%$.

@@

Many have made the claim that building a quantum computing system or quantum communications network will be akin to other major scientific projects such as the Large Hadron Collider (LHC)\index{Large Hadron Collider} at CERN or an array of LIGO gravitational wave detectors for astronomy. However, this analogy is not completely accurate. While LIGO and the LHC are extremely expensive scientific projects, in the case of the LHC there is only \textbf{one} and with LIGO there are only currently \textbf{four} completed operational units. Quantum computing and communications systems will hopefully be ubiquitous in the future. We already know better than to believe, as IBM chairman reputedly did,
\\
\\
\famousquote{I think there is a world market for about five computers.}{Thomas Watson}
\\
\\
Consequently, being able to mass manufacture physical qubits cheaply will be of paramount concern for any hardware developer in this space. And when we say \textit{cheaply}, we really mean it. Physical qubits in a quantum system are often analogised with physical transistors in a classical information processing system. As you can see in Fig.~\ref{fig:price} the cost of individual classical transistors is \textit{insanely} low.

@@

This issue of PPQ is of critical concern for large-scale quantum computing systems. Shown in Fig.~\ref{fig:cost} are costing out of a quantum computing system of sufficient size to perform Shor's factoring algorithm for large key sizes and for quantum simulation of nitrogenase\index{Nitrogenase} molecules for nitrogen fixation. If an ultimate PPQ goal is not \$1 or lower, there may be little economic motivation for building more than a handful of quantum computers globally. It should be noted that PPQ needs to take into account the infrastructure and control systems as well as the physical qubit itself. For example, in superconducting systems, the required dilution refrigeration system is expensive -- around \$500,000. Additionally, the sample chamber for the dilution refrigerator is quite small in comparison to the `footprint' of a superconducting qubit. A commercial dilution refrigeration system can accommodate perhaps 100 such physical qubits. Consequently, at a minimum, the PPQ in this system would be \$5000. Additionally Fig.~\ref{fig:cost} does not include any R\&D expenditure or the costs associated with building the fabrication infrastructure to build the qubits themselves.

@@

\subsection{Operating principles of the quantum Sneakernet}

@@

The answer is the third point noted above -- \textit{information latency}. When we transmit information from one side of the planet to another, we don't want to wait twenty hours for the data to arrive. A classical communications system that has that amount of information latency is unusable for most practical applications. Consequently, our classical infrastructure for communications is designed to operate with high bandwidth (capacity) at as close to the speed of light as physically possible.

@@

Shown in Fig.~\ref{fig:qustick1} is the basic structure of the QuSTICK communications link. Two parties, Alice and Bob each have a QuSTICK. The device itself contains multiple QMUs. Each QMU is chip-set containing sufficient physical qubits to create a long-lived quantum memory of some defined timescale. Referencing back to Fig.~\ref{fig:array}, if the desired memory time is about a day (at a fidelity of 99.99\%), each QMU chipset would consist of approximately 1,600 physical qubits. If we wanted each QMU to protect its respective quantum information for a year, each chip-set would contain approximately 2,100 physical qubits.

@@

Not all QuSTICKS have to go to the same destination. Once the entanglement is prepared at home base, a subset of QuSTICKS may be transported to destination $A$, another subset to destination $B$, and so on. In fact, destination A may be 5km up the road, while destination B is half way around the world. Destination C might use low-cost cargo shipping to receive their QuSTICKs, while destination D's need might be for fewer units sooner, and so shipment by air is preferred (as shown in Fig.~\ref{fig:distribution}). The flexibility enabled by portable quantum memories allows for dynamic allocation of both QuSTICK resources and the use of whatever physical transport method is appropriate to support the final application. This is in contrast to the `one size fits all' approach used by infrastructure-intensive communications systems like satellites and repeaters. Such systems operate in exactly the same way regardless of the demands of the ultimate application.

@@

\subsection{Using and re-charging QuSTICK quantum entanglement}\index{QuSTICK!Re-charing}\index{QuSTICK!Utilisation}

We have described a system where a finite amount of entangled quantum states is maintained by a set of QuSTICKs for a predefined period of time. This period of time needs to be sufficient to entangle the QuSTICKs directly together at the source and physically transport them to the destination. This mechanism now mimics the behaviour of a quantum satellite or quantum repeater system, but with a crucial difference that ultimately makes the Sneakernet system superior from a practical standpoint:
\begin{itemize}
\item The sender and receiver now share a persistent, high fidelity entanglement link that \textbf{does not have to be used immediately}. Quantum satellites and ballistic repeater designs generate entanglement using photons. They are not designed to `store' the entanglement for future use -- the entanglement needs to be consumed for some type of communications protocol immediately upon receipt.
\item The total amount of entanglement a destination shares with home base is dependent only on the number of QMUs and QuSTICKs used. If only 100 entangled states are needed for an application, a single QuSTICK (containing 100 QMU chips) will suffice. One million entangled states would require 10,000 QuSTICKS at 100 QMUs per stick. 
\item The entanglement the Sneakernet provides is \textbf{by design} ultra-high-fidelity. All of the numbers in Fig.~\ref{fig:array} assumes that each QMU can maintain an encoded piece of quantum information for a given period of time \textbf{to a fidelity of 99.99\%}. Increasing the fidelity even further requires only a small increase in the size of the QMU. If a target application requires a fidelity of 99.999999999\% (say for direct connections between fully fault-tolerant quantum computing systems), simply use a few more physical qubits per QMU. i.e. a $T= 22$ week QMU at 99.99\% fidelity requires 2,500 physical qubits, the same $T=22$ week QMU at 99.999999999\% requires 5,400 physical qubits. That's just over double the physical size for 7 orders of magnitude increase in fidelity.
\item Sneakernet entanglement connections can reach global distances (Alice's QuSTICK in Sydney can be connected to Bob's QuSTICK in London using conventional transportation services).
\item The persistent entanglement shared can continue to move before it is used. Alice may not want to use this entanglement in Sydney, but instead transport it to central Australia. The entanglement link with London will continue to move with Alice as long as her QuSTICK provides sufficient error-correction for the additional time required.
\end{itemize}

@@

Instead of physically moving again, Alice and Bob can request an entanglement swap from Alan. Alan will then connect ALAN-1 and ALAN-2 directly together (since he still has physical possession of both units in Berlin) and entangle each of their QMUs. If Alan then measures each of the QMUs in his two QuSTICKs in the $\hat{X}$-basis, the entanglement he initially shared with Alice and Bob is swapped to them. By performing this operation, Alice and Bob can share \textbf{directly} two QuSTICKs of entangled QMUs without ever having to physically meet each other. They can then proceed to perform whatever communications protocol they wish. This swapping protocol is illustrated in Fig.~\ref{fig:SWAPPING}

@@

This kind of flexibility is simply not possible in classical networking design. It would be as if a classical data packet could be sent \textbf{directly} between the Australia and Iceland despite there being no direct telecommunications link between those two countries. Classically, the data packet would have to first travel from Australia to Singapore, then perhaps from Singapore through routers in west Asia, the Middle East, central and northern Europe, the U.K. and finally to Iceland. At any point in its journey the packet might be intercepted, copied, lost, tampered with, inspected, corrupted, or accidentally routed to a completely inaccurate destination.

@@

Once the entanglement in a QuSTICK is consumed and depleted, the owner or operator of the QuSTICK simply has to physically find another QuSTICK that has some entanglement `charge' left. If Alice has no entanglement left, she could go find Charlie (who hasn't consumed his entanglement yet) and physically connect her QuSTICK to his and re-entangle all the QMUs. At this point, Alice has reentered the entanglement network. Once she has, she can use swapping to establish connections to another network member to perform more communications protocols. There is no need for her to reconnect to a central entanglement hub or a distant source that would require her to ship her QuSTICK to the other side of the planet and wait for it to return.

@@

An authentication protocol is generally a small data-exchange mechanism used to confirm that a user is who he says he or she is, and that the information that is to follow will not be coming from a third party or impostor. It is used extensively in classical communications for applications that range from the routine (when I go to www.google.com, am I really talking to Google?) to communications that determine the survival of the human race (did the launch order received by an Ohio-class nuclear submarine really come from the White House?) In a Sneakernet based communications system, authentication tokens will be one of the first applications due to the comparatively small number of QMUs needed.

The key question that the authentication process must answer is this: How do we ensure that messages are coming from the requisite trusted source? Turing's solution is similar to physical authentication tokens that some bank customers are given to access their accounts for high-value transactions. These classical authentication tokens utilise a variety of methods to ensure that the server (e.g. a bank website) and the client (the person with a bank account) can share a secret message that can be used to authenticate a log-in session. Some utilise static password tokens, some use synchronous dynamic tokens and some use a type of `call and response' method. There are even services that use a smart phone APP to verify the phone's SIM card and then generate a one-time key. All of these techniques are vulnerable to security flaws that present themselves if: 1) the implementation is not done perfectly, 2) the token is lost, stolen, or duplicated, or 3) if some classical calculation that was assumed to be computationally difficult is compromised in some way.

@@

\textbf{The design and strength of all key lengths of the AES algorithm (i.e., 128, 192 and 256) are sufficient to protect classified information up to the SECRET level. TOP SECRET information will require use of either the 192 or 256 key lengths. The implementation of AES in products intended to protect national security systems and/or information must be reviewed and certified by NSA prior to their acquisition and use.}

@@

In Fig.~\ref{fig:transistor} we illustrate this assuming Moore's law scaling in the total number of QMUs fabricated (note that Moore's law actually quantifies the number of transistors that can be placed on a single chip; the numbers here are much, much larger). Fig.~\ref{fig:transistor} shows the total number of transistors manufactured per year, worldwide, starting with the first demonstration of the transistor in 1947, until now (source: VSLI research, \href{http://www.vsliresearch.com}{http://www.vsliresearch.com}).

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{transistor}
	\caption{} \label{fig:transistor}
\end{figure}

@@

\subsection{Revisiting the criticisms from GCHQ}\index{GCHQ}

@@

\textbf{QKD protocols address only the problem of agreeing on keys for encrypting data. Ubiquitous on-demand modern services, such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates, rely on authentication and integrity mechanisms (e.g. digital signatures) as well as encryption.}

@@

\textbf{The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission, and the fact that BB84 and similar proposals are fundamentally point-to-point protocols. This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.}

@@

\textbf{Hardware is expensive to obtain and maintain. Unlike software, hardware cannot be patched remotely or cheaply when it degrades or when vulnerabilities are discovered.}

@@

\textbf{Any real-world QKD system will be built from classical components, such as sources, detectors and fibres, and potentially ancillary classical network devices, any one of which may prove to be a weak link. A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.}

@@

\textbf{Denial of service (DoS)\index{Denial of service (DoS) attacks} attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies. Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.}

@@

@@

>>>>

The development of a model for the quantum internet \cite{?} has a distinct advantage over all other communication networks that have preceded it, namely the ability to leverage a treasure trove of information about how global communications systems are used, what are their inefficiencies, their choke points and vulnerabilities. The knowledge that we have gained gives an interesting opportunity in the quantum space, namely, 
\\
\\
\textit{If we had the ability to redesign the classical internet from scratch, how would we do it?}
\\
\\
The hardware that will be needed to transmit quantum information around the globe will be a parallel network to the classical internet as at the very least a fast classical network is still needed to relay the required information to make any quantum communications channel work \cite{?}. So, at a minimum, we can conclude that a global quantum network will be \textit{rate limited} by the classical networking infrastructure that supports it. However, considering that the classical internet currently has the capacity to transmit information at approximately 70\% of the speed of light (in standard silica fibre optics), over global distances and can do so at extremely high data rates means that we will have to work very hard to design and build large-scale quantum networks before the classical side-channel produces any significant bottlenecks.

@@

If these three core points are adhered to, the encrypted message is completely unbreakable by any adversary who may intercept it, regardless of any hypothetical computational resources they may have -- \textit{information-theoretic security}. Unfortunately, the above conditions are simply not practical in most real world situations. 
\begin{itemize}
\item Generating a random bit string, in the true definition of random, has only become technologically possible in the past decade or two as result of quantum technology. Quantum random number generators use the intrinsic randomness of quantum mechanical processes to generate random bit strings that for all intents and purposes are sufficient for one time pads. These devices can now be bought as off the shelf units with varying degrees of quality. 
\item Avoiding the reuse of a key can, in principle, be adhered to, but satisfying this requirement may be economically or logistically impractical. Avoiding reuse becomes even more difficult when the message to be encrypted is big. There are many examples of technology in the field that require secure, high data-rate transmission. Video footage from helicopters or drones is a good example. A drone equipped with a high-resolution 4K camera system needs to be able to transmit information at a rate of 764GB/hour uncompressed. This would require the same rate of one-time-pad material to be generated and shared between Alice and Bob to ensure a secure connection of the video stream. None of this material could be used even a second time. 
\item The third and most vulnerable constraint is the sharing of key information between Alice and Bob in a manner that can be guaranteed to have never been compromised. This is complicated by the fact that Alice and Bob in almost all practical situations will not be in physical contact with each other prior to sharing an encrypted message. How can we exchange a large amount of key material between two parties who have never met in such a way that we can be as certain as humanly possible that the key information was not revealed, sold, copied or otherwise accessed by a third party? The third party may even be authorised to have access to the key information. This would immediately destroy the \textit{perfectly implemented} assumption underlying the security of the one-time-pad. 
\end{itemize}

@@

For extremely sensitive tasks, key exchange and security is usually achieved through some combination of segregated networking and obfuscation. Here are some examples:

@@

\subsection{QKD vs classical key exchange}\index{Classical key exchange}

A 2016 assessment from the UK's cyber intelligence agency GCHQ\index{GCHQ} references four concerns with QKD as an effective replacement for classical techniques:
\begin{itemize}
\item \textit{QKD protocols address only the problem of agreeing on keys for encrypting data.} Ubiquitous on-demand modern services (such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates) rely more on authentication and integrity mechanisms — such as digital signatures — than on encryption.
\item \textit{The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission and the fact that BB84 and similar proposals are fundamentally point-to-point protocols.} This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.
\item \textit{Hardware is relatively expensive to obtain and maintain.} Unlike software, hardware cannot be patched remotely or cheaply when it degrades or when vulnerabilities are discovered.
\item \textit{Any real-world QKD system will be built from classical components, such as sources, detectors, fibres, and ancillary classical network devices, any one of which may prove to be a weak link.} A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.
\item \textit{Denial of service (DoS) attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies.} Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.
\end{itemize}

@@

Colour centres, at least from the context of building large-portable qubit arrays, appear the most promising -- mostly due to to the large-scale infrastructure needed for the technology. In colour centres, an atomic defect is inserted within a crystal substrate -- for example, a Nitrogen defect in a perfect diamond crystal of Carbon -- which provides what is known as a \textit{spin vacuum} substrate. Essentially, the surrounding crystal itself provides the same isolation properties that an actual physical vacuum does in, for example, ion-trap technology. Additionally, many colour centres are operated at temperatures of only 4K. While still cold, 4K cryogenic technology is far simpler than the dilution refrigeration systems needed for a 30mK thermal environment. 4K cryogenic technology is so advanced that we are able to effectively launch these sorts of cooling systems into space. Thirdly, colour centres are generally \textit{optically accessible.}. An optically accessible colour centre has, in general, an electronic transition of the donor system that is resonant at optical frequencies. This allows for remote coupling of colour centres using optical photons which are comparatively easy to route in and out of the crystal and surrounding 4K infrastructure -- in comparison to superconducting qubits which interact with microwave photons which are difficult to route around or systems such as Phosphorus in Silicon that generally utilise direct dipole/dipole or exchange-based coupling to realise gates.

@@

The surface code has been extremely well studied over the past 15 years. We have extremely accurate simulations that detail the threshold behaviour of the code under a variety of different assumptions and we have quantified very well how the scaling of the code behaves as a function of physical error rate. For this reason we are able to quantify expected \textit{logical} memory time, $T$, in terms of the physical operation time of the quantum gates in our hardware, $t$, the number of physical qubits in the QMU array, $N$, and the logical error rate we want to target, $P$. Through direct numerical simulation, we find,
\begin{align} \label{eq:scale}
T \approx 10t\sqrt{N} P(70p)^{-\sqrt{N}/4},
\end{align}
where $p$ is the physical error rate associated with each of the qubits within each QMU -- assumed to be at least below the fault-tolerant threshold of the planar code, $p_\mathrm{th} \approx 0.7\%$.

@@

Many have made the claim that building a quantum computing system or quantum communications network will be akin to other major scientific projects such as the Large Hadron Collider (LHC)\index{Large Hadron Collider} at CERN\index{CERN} or an array of LIGO\index{LIGO} gravitational wave detectors for astronomy. However, this analogy is not completely accurate. While LIGO and the LHC are extremely expensive scientific projects, in the case of the LHC there is only one and with LIGO there are only currently four completed operational units. Quantum computing and communications systems will hopefully be ubiquitous in the future. We already know better than to believe, as IBM chairman reputedly did,
\\
\\
\famousquote{I think there is a world market for about five computers.}{Thomas Watson}
\\
\\
Consequently, being able to mass manufacture physical qubits cheaply will be of paramount concern for any hardware developer in this space. And when we say \textit{cheaply}, we really mean it. Physical qubits in a quantum system are often analogised with physical transistors in a classical information processing system. As you can see in Fig.~\ref{fig:price} the cost of individual classical transistors is \textit{insanely} low.

@@

This issue of PPQ is of critical concern for large-scale quantum computing systems. Shown in Fig.~\ref{fig:price} are costing out of a quantum computing system of sufficient size to perform Shor's factoring algorithm for large key sizes and for quantum simulation of nitrogenase\index{Nitrogenase} molecules for nitrogen fixation. If an ultimate PPQ goal is not \$1 or lower, there may be little economic motivation for building more than a handful of quantum computers globally. It should be noted that PPQ needs to take into account the infrastructure and control systems as well as the physical qubit itself. For example, in superconducting systems, the required dilution refrigeration system is expensive -- around \$500,000. Additionally, the sample chamber for the dilution refrigerator is quite small in comparison to the `footprint' of a superconducting qubit. A commercial dilution refrigeration system can accommodate perhaps 100 such physical qubits. Consequently, at a minimum, the PPQ in this system would be \$5,000. Additionally Fig.~\ref{fig:price} does not include any R\&D expenditure or the costs associated with building the fabrication infrastructure to build the qubits themselves.

@@

\subsection{Operating principles}

@@

The answer is the third point noted above -- \textit{information latency}\index{Latency}. When we transmit information from one side of the planet to another, we don't want to wait twenty hours for the data to arrive. A classical communications system that has that amount of information latency is unusable for most practical applications. Consequently, our classical infrastructure for communications is designed to operate with high bandwidth (capacity) at as close to the speed of light as physically possible.

@@

Shown in Fig.~\ref{fig:qustick1} is the basic structure of the QuSTICK communications link. Two parties, Alice and Bob each have a QuSTICK. The device itself contains multiple QMUs. Each QMU is chip-set containing sufficient physical qubits to create a long-lived quantum memory of some defined timescale. Referencing back to Fig.~\ref{fig:array}, if the desired memory time is about a day (at a fidelity of $99.99\%$), each QMU chipset would consist of approximately 1,600 physical qubits. If we wanted each QMU to protect its respective quantum information for a year, each chip-set would contain approximately 2,100 physical qubits.

@@

Not all QuSTICKS have to go to the same destination. Once the entanglement is prepared at home base, a subset of QuSTICKS may be transported to destination $A$, another subset to destination $B$, and so on. In fact, destination $A$ may be 5km up the road, while destination $B$ is half way around the world. Destination $C$ might use low-cost cargo shipping to receive their QuSTICKs, while destination $D$'s need might be for fewer units sooner, and so shipment by air is preferred (as shown in Fig.~\ref{fig:distribution}). The flexibility enabled by portable quantum memories allows for dynamic allocation of both QuSTICK resources and the use of whatever physical transport method is appropriate to support the final application. This is in contrast to the `one size fits all' approach used by infrastructure-intensive communications systems like satellites and repeaters. Such systems operate in exactly the same way regardless of the demands of the ultimate application.

@@

\subsection{Utilising \& re-charging QuSTICKs}\index{QuSTICK!Re-charing}\index{QuSTICK!Utilisation}

We have described a system where a finite amount of entangled quantum states is maintained by a set of QuSTICKs for a predefined period of time. This period of time needs to be sufficient to entangle the QuSTICKs directly together at the source and physically transport them to the destination. This mechanism now mimics the behaviour of a quantum satellite or quantum repeater system, but with a crucial difference that ultimately makes the Sneakernet system superior from a practical standpoint:
\begin{itemize}
\item The sender and receiver now share a persistent, high fidelity entanglement link that \textit{does not have to be used immediately}. Quantum satellites and ballistic repeater designs generate entanglement using photons. They are not designed to `store' the entanglement for future use -- the entanglement needs to be consumed for some type of communications protocol immediately upon receipt.
\item The total amount of entanglement a destination shares with home base is dependent only on the number of QMUs and QuSTICKs used. If only 100 entangled states are needed for an application, a single QuSTICK (containing 100 QMU chips) will suffice. One million entangled states would require 10,000 QuSTICKS at 100 QMUs per stick. 
\item The entanglement the Sneakernet provides is \textit{by design} ultra-high-fidelity. All of the numbers in Fig.~\ref{fig:array} assumes that each QMU can maintain an encoded piece of quantum information for a given period of time \textit{to a fidelity of $99.99\%$}. Increasing the fidelity even further requires only a small increase in the size of the QMU. If a target application requires a fidelity of 99.999999999\% (say for direct connections between fully fault-tolerant quantum computing systems), simply use a few more physical qubits per QMU. i.e. a $T= 22$ week QMU at 99.99\% fidelity requires 2,500 physical qubits, the same $T=22$ week QMU at fidelity $99.999999999\%$ requires 5,400 physical qubits. That's just over double the physical size for 7 orders of magnitude increase in fidelity.
\item Sneakernet entanglement connections can reach global distances (Alice's QuSTICK in Sydney can be connected to Bob's QuSTICK in London using conventional transportation services).
\item The persistent entanglement shared can continue to move before it is used. Alice may not want to use this entanglement in Sydney, but instead transport it to central Australia. The entanglement link with London will continue to move with Alice as long as her QuSTICK provides sufficient error-correction for the additional time required.
\end{itemize}

@@

Instead of physically moving again, Alice and Bob can request an entanglement swap from Alan. Alan will then connect ALAN-1 and ALAN-2 directly together (since he still has physical possession of both units in Berlin) and entangle each of their QMUs. If Alan then measures each of the QMUs in his two QuSTICKs in the $\hat{X}$-basis, the entanglement he initially shared with Alice and Bob is swapped to them. By performing this operation, Alice and Bob can \textit{directly} share two QuSTICKs of entangled QMUs without ever having to physically meet each other. They can then proceed to perform whatever communications protocol they wish. This swapping protocol is illustrated in Fig.~\ref{fig:SWAPPING}

@@

This kind of flexibility is simply not possible in classical networking design. It would be as if a classical data packet could be sent \textit{directly} between the Australia and Iceland despite there being no direct telecommunications link between those two countries. Classically, the data packet would have to first travel from Australia to Singapore, then perhaps from Singapore through routers in west Asia, the Middle East, central and northern Europe, the UK and finally to Iceland. At any point in its journey the packet might be intercepted, copied, lost, tampered with, inspected, corrupted, or accidentally routed to a completely inaccurate destination.

@@

Once the entanglement in a QuSTICK is consumed and depleted, the owner or operator of the QuSTICK simply has to physically find another QuSTICK that has some entanglement `charge' left\index{Entanglement!Charge}. If Alice has no entanglement left, she could go find Charlie (who hasn't consumed his entanglement yet) and physically connect her QuSTICK to his and re-entangle all the QMUs. At this point, Alice has reentered the entanglement network. Once she has, she can use swapping to establish connections to another network member to perform more communications protocols. There is no need for her to reconnect to a central entanglement hub or a distant source that would require her to ship her QuSTICK to the other side of the planet and wait for it to return.

@@

An authentication protocol is generally a small data-exchange mechanism used to confirm that a user is who he says he or she is, and that the information that is to follow will not be coming from a third party or impostor. It is used extensively in classical communications for applications that range from the routine (when I visit \href{href://www.google.com}{http://www.google.com}, am I really talking to Google?) to communications that determine the survival of the human race (did the launch order received by an Ohio-class nuclear submarine really come from the White House?) In a Sneakernet based communications system, authentication tokens will be one of the first applications due to the comparatively small number of QMUs needed.

The key question that the authentication process must answer is this: How do we ensure that messages are coming from the requisite trusted source? Turing's solution is similar to physical authentication tokens that some bank customers are given to access their accounts for high-value transactions. These classical authentication tokens utilise a variety of methods to ensure that the server (e.g. a bank website) and the client (the person with a bank account) can share a secret message that can be used to authenticate a log-in session. Some utilise static password tokens, some use synchronous dynamic tokens and some use a type of `call and response' method. There are even services that use a smart phone APP to verify the phone's SIM card and then generate a one-time key. All of these techniques are vulnerable to security flaws that present themselves if:
\begin{enumerate}
\item The implementation is imperfect.
\item The token is lost, stolen, or duplicated.
\item If some classical calculation that was assumed to be computationally difficult is compromised in some way. 
\end{enumerate}

@@

The design and strength of all key lengths of the AES\index{AES} algorithm (i.e. 128, 192 and 256 bits) are sufficient to protect classified information up to the \textsc{SECRET} level. \textsc{TOP SECRET} information mandates use of either 192 or 256 key lengths. The implementation of AES in products intended to protect national security systems and/or information must be reviewed and certified by the NSA\index{NSA} prior to their acquisition and use.

@@

In Fig.~\ref{fig:transistor} we illustrate this assuming Moore's law scaling in the total number of QMUs fabricated (note that Moore's law actually quantifies the number of transistors that can be placed on a single chip; the numbers here are much, much larger). Fig.~\ref{fig:transistor} shows the total number of transistors manufactured per year, worldwide, starting with the first demonstration of the transistor in 1947, until now.

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{transistor}
	\caption{(source: VSLI research, \href{http://www.vsliresearch.com}{http://www.vsliresearch.com})} \label{fig:transistor}
\end{figure}

@@

\subsection{Revisiting the GCHQ criticisms}\index{GCHQ}

@@

QKD protocols address only the problem of agreeing on keys for encrypting data. Ubiquitous on-demand modern services, such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates, rely on authentication and integrity mechanisms (e.g. digital signatures) as well as encryption.

@@

The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission, and the fact that BB84 and similar proposals are fundamentally point-to-point protocols. This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.

@@

Hardware is expensive to obtain and maintain. Unlike software, hardware cannot be patched remotely or cheaply when it degrades or when vulnerabilities are discovered.

@@

Any real-world QKD system will be built from classical components, such as sources, detectors and fibres, and potentially ancillary classical network devices, any one of which may prove to be a weak link. A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.

@@

Denial of service (DoS)\index{Denial of service (DoS) attacks} attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies. Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.

@@

\subsection{The ups and downs of the quantum Sneakernet}

\comment{To do}

\comment{No interception, bandwidth, dos requires destroying endpoints since no channels}

@@

\section{Moore's Law in the quantum era}\index{Quantum Moore's Law}

\comment{To do}
